Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
Wrap up time step discussion

Time step dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final time step chosen to run the
simulations.

\todo[inline]{Find some examples in the literature where time steps are much
    larger.}

>>>>

Time step dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum
at $\Delta t = 0.002$ s, with some divergence for smaller time steps. The local
minimum was chosen as the final time step to run the simulations. Note that the
SST model's convergence behavior may be due to its specific implementation in
\textit{OpenFOAM}, and not indicative of the nature of the model equations.
Verification studies for CFTs with this level of detail in the literature are
not common, though the final time step is comparable to others
\cite{Balduzzi2016}.
